\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-20 paper/tables/stmTopWords120_2.tex
added new results for model with 120 topics

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Sun Aug  5 19:55:00 2018

@@

 34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 
   82 & \cellcolor{white}com & \cellcolor{white}mar & \cellcolor{white}spec & \cellcolor{white}jun & \cellcolor{white}est & \cellcolor{white}comm & \mybar{1388} \\ 
   22 & \cellcolor{white}server & \cellcolor{white}software & \cellcolor{white}wireless & \cellcolor{white}technology & \cellcolor{white}desktop & \cellcolor{white}broadband & \mybar{430} \\ 
   80 & \cellcolor{white}artist & \cellcolor{white}art & \cellcolor{white}artwork & \cellcolor{white}exhibition & \cellcolor{white}artistic & \cellcolor{white}sculpture & \mybar{1099} \\ 
  113 & \cellcolor{white}trench & \cellcolor{white}thickness & \cellcolor{white}compaction & \cellcolor{white}concrete & \cellcolor{white}slab & \cellcolor{white}excavation & \mybar{766} \\ 
   87 & \cellcolor{white}respondent & \cellcolor{white}survey & \cellcolor{white}census & \cellcolor{white}racial & \cellcolor{white}demographic & \cellcolor{white}score & \mybar{427} \\ 
   83 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}supportive & \cellcolor{white}client & \cellcolor{white}transitional & \cellcolor{white}encampment & \mybar{229} \\ 
   20 & \cellcolor{white}noise & \cellcolor{white}fugitive & \cellcolor{white}receptor & \cellcolor{white}exhaust & \cellcolor{white}vibration & \cellcolor{white}emission & \mybar{376} \\ 
   35 & \cellcolor{white}landlord & \cellcolor{white}tenant & \cellcolor{white}owner & \cellcolor{white}property & \cellcolor{white}rent & \cellcolor{white}lien & \mybar{205} \\ 
  105 & \cellcolor{white}beach & \cellcolor{white}orange & \cellcolor{white}arena & \cellcolor{white}rainier & \cellcolor{white}ocean & \cellcolor{white}resort & \mybar{457} \\ 
    2 & \cellcolor{blue!10}yon & \cellcolor{blue!10}bay & \cellcolor{blue!10}gen & \cellcolor{blue!10}sou & \cellcolor{blue!10}coliseum & \cellcolor{blue!10}estuary & \mybar{385} \\ 
    6 & \cellcolor{white}redevelopment & \cellcolor{white}land & \cellcolor{white}developer & \cellcolor{white}parcel & \cellcolor{white}development & \cellcolor{white}area & \mybar{70} \\ 
  104 & \cellcolor{white}riparian & \cellcolor{white}wetland & \cellcolor{white}habitat & \cellcolor{white}marsh & \cellcolor{white}floodplain & \cellcolor{white}grassland & \mybar{968} \\ 
   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}deduction & \cellcolor{white}levy & \cellcolor{white}taxpayer & \mybar{172} \\ 
   68 & \cellcolor{white}economy & \cellcolor{white}workforce & \cellcolor{white}economic & \cellcolor{white}sector & \cellcolor{white}industry & \cellcolor{white}innovation & \mybar{332} \\ 
   28 & \cellcolor{white}figure & \cellcolor{white}table & \cellcolor{white}scenario & \cellcolor{white}margin & \cellcolor{white}analysis & \cellcolor{white}appendix & \mybar{207} \\ 
  110 & \cellcolor{white}bond & \cellcolor{white}maturity & \cellcolor{white}debt & \cellcolor{white}issuer & \cellcolor{white}redemption & \cellcolor{white}obligation & \mybar{232} \\ 
  102 & \cellcolor{white}sidewalk & \cellcolor{white}curb & \cellcolor{white}pole & \cellcolor{white}crosswalk & \cellcolor{white}ramp & \cellcolor{white}sign & \mybar{237} \\ 
  118 & \cellcolor{blue!10}project & \cellcolor{blue!10}phase & \cellcolor{blue!10}construction & \cellcolor{blue!10}completion & \cellcolor{blue!10}improvement & \cellcolor{blue!10}complete & \mybar{45} \\ 
   78 & \cellcolor{blue!10}parking & \cellcolor{blue!10}tow & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}garage & \cellcolor{blue!10}car & \cellcolor{blue!10}motor & \mybar{210} \\ 
   71 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}retiree & \cellcolor{blue!10}retirement & \cellcolor{blue!10}pension & \cellcolor{blue!10}deductible & \cellcolor{blue!10}unfunded & \mybar{239} \\ 
   91 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}deer & \cellcolor{blue!10}shrub & \cellcolor{blue!10}planting & \mybar{1240} \\ 
  114 & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}exam & \cellcolor{blue!10}supervision & \cellcolor{blue!10}supervise & \cellcolor{blue!10}examination & \cellcolor{blue!10}ability & \mybar{432} \\ 
   16 & \cellcolor{blue!10}park & \cellcolor{blue!10}recreation & \cellcolor{blue!10}playground & \cellcolor{blue!10}zoo & \cellcolor{blue!10}trail & \cellcolor{blue!10}picnic & \mybar{290} \\ 
   53 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}boat & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}maritime & \cellcolor{blue!10}dock & \cellcolor{blue!10}barge & \mybar{800} \\ 
   76 & \cellcolor{blue!10}felony & \cellcolor{blue!10}violent & \cellcolor{blue!10}offender & \cellcolor{blue!10}gang & \cellcolor{blue!10}theft & \cellcolor{blue!10}inmate & \mybar{783} \\ 
    4 & \cellcolor{blue!10}courtyard & \cellcolor{blue!10}realm & \cellcolor{blue!10}design & \cellcolor{blue!10}facade & \cellcolor{blue!10}proponent & \cellcolor{blue!10}articulation & \mybar{608} \\ 
  100 & \cellcolor{blue!10}division & \cellcolor{blue!10}manage & \cellcolor{blue!10}staffing & \cellcolor{blue!10}oversee & \cellcolor{blue!10}management & \cellcolor{blue!10}analyst & \mybar{100} \\ 
   97 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}alternative & \cellcolor{blue!10}propose & \mybar{132} \\ 
   11 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}preservation & \cellcolor{blue!10}historical & \mybar{876} \\ 
   77 & \cellcolor{blue!10}million & \cellcolor{blue!10}fiscal & \cellcolor{blue!10}forecast & \cellcolor{blue!10}revenue & \cellcolor{blue!10}quarter & \cellcolor{blue!10}billion & \mybar{138} \\ 
   74 & \cellcolor{blue!10}board & \cellcolor{blue!10}chairperson & \cellcolor{blue!10}secretary & \cellcolor{blue!10}member & \cellcolor{blue!10}appoint & \cellcolor{blue!10}executive & \mybar{118} \\ 
   47 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}bias & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \mybar{580} \\ 
   92 & \cellcolor{blue!10}sick & \cellcolor{blue!10}employee & \cellcolor{blue!10}wage & \cellcolor{blue!10}overtime & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{260} \\ 
   10 & \cellcolor{blue!10}ave & \cellcolor{blue!10}avenue & \cellcolor{blue!10}south & \cellcolor{blue!10}east & \cellcolor{blue!10}west & \cellcolor{blue!10}blvd & \mybar{189} \\ 
  112 & \cellcolor{blue!10}grant & \cellcolor{blue!10}loan & \cellcolor{blue!10}funding & \cellcolor{blue!10}program & \cellcolor{blue!10}recipient & \cellcolor{blue!10}federal & \mybar{85} \\ 
   56 & \cellcolor{blue!10}downtown & \cellcolor{blue!10}mall & \cellcolor{blue!10}midtown & \cellcolor{blue!10}uptown & \cellcolor{blue!10}hotel & \cellcolor{blue!10}shopping & \mybar{414} \\ 
   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}successor & \cellcolor{blue!10}oversight & \cellcolor{blue!10}attachment & \cellcolor{blue!10}describe & \mybar{125} \\ 
   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}transit & \cellcolor{blue!10}bicyclist & \cellcolor{blue!10}lane & \cellcolor{blue!10}bus & \mybar{315} \\ 
   62 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}income & \cellcolor{blue!10}household & \cellcolor{blue!10}moderate & \mybar{188} \\ 
   99 & \cellcolor{blue!10}memorandum & \cellcolor{blue!10}resolution & \cellcolor{blue!10}council & \cellcolor{blue!10}legislation & \cellcolor{blue!10}entitle & \cellcolor{blue!10}commission & \mybar{173} \\ 
   19 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}accounting & \cellcolor{blue!10}asset & \cellcolor{blue!10}statement & \cellcolor{blue!10}financial & \cellcolor{blue!10}net & \mybar{156} \\ 
  103 & \cellcolor{blue!10}permission & \cellcolor{blue!10}ayes & \cellcolor{blue!10}correspondence & \cellcolor{blue!10}bid & \cellcolor{blue!10}smith & \cellcolor{blue!10}demolition & \mybar{203} \\ 
  107 & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}dollars & \cellcolor{blue!10}thousand & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}matrix & \cellcolor{blue!10}justification & \mybar{117} \\ 
   12 & \cellcolor{blue!10}approach & \cellcolor{blue!10}difficult & \cellcolor{blue!10}achieve & \cellcolor{blue!10}challenge & \cellcolor{blue!10}critical & \cellcolor{blue!10}often & \mybar{257} \\ 
   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}fence & \cellcolor{blue!10}setback & \cellcolor{blue!10}exception & \cellcolor{blue!10}yard & \cellcolor{blue!10}applicant & \mybar{136} \\ 
   90 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}procedure & \cellcolor{blue!10}internal & \cellcolor{blue!10}auditing & \cellcolor{blue!10}documentation & \mybar{226} \\ 
   64 & \cellcolor{blue!10}density & \cellcolor{blue!10}urban & \cellcolor{blue!10}corridor & \cellcolor{blue!10}village & \cellcolor{blue!10}orient & \cellcolor{blue!10}transit & \mybar{165} \\ 
   21 & \cellcolor{blue!10}goal & \cellcolor{blue!10}strategy & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}implementation & \mybar{105} \\ 
   73 & \cellcolor{blue!10}parish & \cellcolor{blue!10}rouge & \cellcolor{blue!10}baton & \cellcolor{blue!10}hogan & \cellcolor{blue!10}councilman & \cellcolor{blue!10}thereto & \mybar{482} \\ 
   29 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}discussion & \cellcolor{blue!10}feedback & \cellcolor{blue!10}discuss & \cellcolor{blue!10}presentation & \mybar{168} \\ 
   32 & \cellcolor{blue!10}budget & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}appropriation & \cellcolor{blue!10}fund & \cellcolor{blue!10}endorse & \cellcolor{blue!10}balance & \mybar{129} \\ 
   54 & \cellcolor{blue!10}aye & \cellcolor{blue!10}absent & \cellcolor{blue!10}khan & \cellcolor{blue!10}nay & \cellcolor{blue!10}berry & \cellcolor{blue!10}voting & \mybar{344} \\ 
   39 & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}tab & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}alt & \mybar{117} \\ 
  109 & \cellcolor{blue!10}auburn & \cellcolor{blue!10}buffalo & \cellcolor{blue!10}ward & \cellcolor{blue!10}brown & \cellcolor{blue!10}announce & \cellcolor{blue!10}casino & \mybar{177} \\ 
   50 & \cellcolor{blue!10}news & \cellcolor{blue!10}warren & \cellcolor{blue!10}lovely & \cellcolor{blue!10}release & \cellcolor{blue!10}leader & \cellcolor{blue!10}proud & \mybar{498} \\ 
   79 & \cellcolor{blue!20}digest & \cellcolor{blue!20}proposal & \cellcolor{blue!20}sander & \cellcolor{blue!20}reappoints & \cellcolor{blue!20}metropolitan & \cellcolor{blue!20}gray & \mybar{236} \\ 
   27 & \cellcolor{blue!20}bankruptcy & \cellcolor{blue!20}plaintiff & \cellcolor{blue!20}creditor & \cellcolor{blue!20}trial & \cellcolor{blue!20}court & \cellcolor{blue!20}supreme & \mybar{810} \\ 
   31 & \cellcolor{blue!20}agenda & \cellcolor{blue!20}speaker & \cellcolor{blue!20}item & \cellcolor{blue!20}committee & \cellcolor{blue!20}chair & \cellcolor{blue!20}divided & \mybar{146} \\ 
   48 & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}reinvestment & \cellcolor{blue!20}inc & \cellcolor{blue!20}contract & \cellcolor{blue!20}authorize & \mybar{134} \\ 
   55 & \cellcolor{blue!80}suspect & \cellcolor{blue!80}shoot & \cellcolor{blue!80}fatal & \cellcolor{blue!80}homicide & \cellcolor{blue!80}stopper & \cellcolor{blue!80}pronounce & \mybar{512} \\ 

@@

>>>>

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon May 20 11:38:16 2019

@@

 29 & \cellcolor{blue!10}labor & \cellcolor{blue!10}worker & \cellcolor{blue!10}force & \cellcolor{blue!10}unemployed & \cellcolor{blue!10}earnings & \cellcolor{blue!10}civilian & \mybar{80} \\ 
  111 & \cellcolor{blue!10}discharge & \cellcolor{blue!10}pollutant & \cellcolor{blue!10}inspection & \cellcolor{blue!10}inspect & \cellcolor{blue!10}pollution & \cellcolor{blue!10}inspector & \mybar{109} \\ 
   68 & \cellcolor{blue!10}contractual & \cellcolor{blue!10}parts & \cellcolor{blue!10}duke & \cellcolor{blue!10}outside & \cellcolor{blue!10}postage & \cellcolor{blue!10}receipts & \mybar{274} \\ 
   77 & \cellcolor{blue!10}curb & \cellcolor{blue!10}pavement & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}ramp & \cellcolor{blue!10}gutter & \cellcolor{blue!10}asphalt & \mybar{390} \\ 
   65 & \cellcolor{blue!10}draft & \cellcolor{blue!10}update & \cellcolor{blue!10}process & \cellcolor{blue!10}review & \cellcolor{blue!10}staff & \cellcolor{blue!10}progress & \mybar{67} \\ 
   24 & \cellcolor{blue!10}landlord & \cellcolor{blue!10}tenant & \cellcolor{blue!10}renewal & \cellcolor{blue!10}rent & \cellcolor{blue!10}lease & \cellcolor{blue!10}expired & \mybar{255} \\ 
  106 & \cellcolor{blue!10}consultant & \cellcolor{blue!10}proposer & \cellcolor{blue!10}procurement & \cellcolor{blue!10}contract & \cellcolor{blue!10}firm & \cellcolor{blue!10}subcontractor & \mybar{179} \\ 
   43 & \cellcolor{blue!10}blanket & \cellcolor{blue!10}medicare & \cellcolor{blue!10}payroll & \cellcolor{blue!10}premium & \cellcolor{blue!10}undistributed & \cellcolor{blue!10}refund & \mybar{107} \\ 
  103 & \cellcolor{white}urban & \cellcolor{white}mixed & \cellcolor{white}density & \cellcolor{white}redevelopment & \cellcolor{white}development & \cellcolor{white}industrial & \mybar{115} \\ 
   89 & \cellcolor{blue!10}taxable & \cellcolor{blue!10}res & \cellcolor{blue!10}deed & \cellcolor{blue!10}value & \cellcolor{blue!10}homestead & \cellcolor{blue!10}star & \mybar{41} \\ 
   83 & \cellcolor{blue!10}building & \cellcolor{blue!10}demolition & \cellcolor{blue!10}story & \cellcolor{blue!10}demolish & \cellcolor{blue!10}floor & \cellcolor{blue!10}build & \mybar{82} \\ 
  119 & \cellcolor{blue!10}cost & \cellcolor{blue!10}estimate & \cellcolor{blue!10}estimated & \cellcolor{blue!10}initial & \cellcolor{blue!10}costs & \cellcolor{blue!10}change & \mybar{52} \\ 
  109 & \cellcolor{blue!10}respondent & \cellcolor{blue!10}satisfied & \cellcolor{blue!10}dissatisfied & \cellcolor{blue!10}survey & \cellcolor{blue!10}satisfaction & \cellcolor{blue!10}disagree & \mybar{403} \\ 
   64 & \cellcolor{blue!10}must & \cellcolor{blue!10}signature & \cellcolor{blue!10}copy & \cellcolor{blue!10}application & \cellcolor{blue!10}applicant & \cellcolor{blue!10}submission & \mybar{139} \\ 
   26 & \cellcolor{blue!10}tax & \cellcolor{blue!10}deduction & \cellcolor{blue!10}amt & \cellcolor{blue!10}assessed & \cellcolor{blue!10}bill & \cellcolor{blue!10}abatement & \mybar{171} \\ 
   78 & \cellcolor{blue!10}yes & \cellcolor{blue!10}worksheet & \cellcolor{blue!10}text & \cellcolor{blue!10}pic & \cellcolor{blue!10}font & \cellcolor{blue!10}button & \mybar{476} \\ 
    7 & \cellcolor{blue!10}greenhouse & \cellcolor{blue!10}emission & \cellcolor{blue!10}coal & \cellcolor{blue!10}climate & \cellcolor{blue!10}ozone & \cellcolor{blue!10}dioxide & \mybar{334} \\ 
   54 & \cellcolor{blue!10}parking & \cellcolor{blue!10}tow & \cellcolor{blue!10}taxi & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}shuttle & \cellcolor{blue!10}passenger & \mybar{236} \\ 
   41 & \cellcolor{blue!10}assistant & \cellcolor{blue!10}analyst & \cellcolor{blue!10}technician & \cellcolor{blue!10}aide & \cellcolor{blue!10}specialist & \cellcolor{blue!10}asst & \mybar{119} \\ 
   22 & \cellcolor{blue!10}allocation & \cellcolor{blue!10}val & \cellcolor{blue!10}cove & \cellcolor{blue!10}acct & \cellcolor{blue!10}glen & \cellcolor{blue!10}subtotal & \mybar{79} \\ 
   63 & \cellcolor{blue!10}fee & \cellcolor{blue!10}charge & \cellcolor{blue!10}license & \cellcolor{blue!10}reservation & \cellcolor{blue!10}surcharge & \cellcolor{blue!10}refundable & \mybar{143} \\ 
  117 & \cellcolor{blue!10}delay & \cellcolor{blue!10}perm & \cellcolor{blue!10}queue & \cellcolor{blue!10}peak & \cellcolor{blue!10}flt & \cellcolor{blue!10}detector & \mybar{113} \\ 
    4 & \cellcolor{blue!10}datum & \cellcolor{blue!10}database & \cellcolor{blue!10}copyright & \cellcolor{blue!10}accuracy & \cellcolor{blue!10}data & \cellcolor{blue!10}compile & \mybar{193} \\ 
   45 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}auditing & \cellcolor{blue!10}internal & \cellcolor{blue!10}implemented & \cellcolor{blue!10}procedure & \mybar{222} \\ 
  100 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}significant & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significance & \cellcolor{blue!10}unavoidable & \mybar{136} \\ 
   88 & \cellcolor{blue!10}gender & \cellcolor{blue!10}discrimination & \cellcolor{blue!10}transgender & \cellcolor{blue!10}immigrant & \cellcolor{blue!10}immigration & \cellcolor{blue!10}religion & \mybar{859} \\ 
    9 & \cellcolor{blue!10}district & \cellcolor{blue!10}zoning & \cellcolor{blue!10}maker & \cellcolor{blue!10}vacancy & \cellcolor{blue!10}speaker & \cellcolor{blue!10}planner & \mybar{45} \\ 
   12 & \cellcolor{blue!10}artist & \cellcolor{blue!10}artwork & \cellcolor{blue!10}art & \cellcolor{blue!10}arts & \cellcolor{blue!10}mural & \cellcolor{blue!10}sculpture & \mybar{1055} \\ 
   94 & \cellcolor{blue!10}contracted & \cellcolor{blue!10}encumbrance & \cellcolor{blue!10}unencumbered & \cellcolor{blue!10}exp & \cellcolor{blue!10}expend & \cellcolor{blue!10}bud & \mybar{71} \\ 
  110 & \cellcolor{blue!10}rouge & \cellcolor{blue!10}parish & \cellcolor{blue!10}baton & \cellcolor{blue!10}thereto & \cellcolor{blue!10}sewerage & \cellcolor{blue!10}adjudicate & \mybar{464} \\ 
   46 & \cellcolor{blue!10}commissioner & \cellcolor{blue!10}chair & \cellcolor{blue!10}commission & \cellcolor{blue!10}committee & \cellcolor{blue!10}briefing & \cellcolor{blue!10}advisory & \mybar{187} \\ 
   85 & \cellcolor{blue!10}sch & \cellcolor{blue!10}min & \cellcolor{blue!10}tin & \cellcolor{blue!10}hump & \cellcolor{blue!10}carpool & \cellcolor{blue!10}qua & \mybar{390} \\ 
   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}allege & \cellcolor{blue!10}complaint & \cellcolor{blue!10}doc & \cellcolor{blue!10}misconduct & \mybar{963} \\ 
   30 & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}examination & \cellcolor{blue!10}supervision & \cellcolor{blue!10}knowledge & \cellcolor{blue!10}exam & \cellcolor{blue!10}ability & \mybar{410} \\ 
  107 & \cellcolor{blue!10}savings & \cellcolor{blue!10}ltd & \cellcolor{blue!10}village & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}excise & \cellcolor{blue!10}costs & \mybar{81} \\ 
   72 & \cellcolor{blue!10}imp & \cellcolor{blue!10}burglary & \cellcolor{blue!10}theft & \cellcolor{blue!10}testify & \cellcolor{blue!10}petitioner & \cellcolor{blue!10}mischief & \mybar{116} \\ 
   60 & \cellcolor{blue!10}bike & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bicyclist & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}route & \cellcolor{blue!10}mobility & \mybar{336} \\ 
   82 & \cellcolor{blue!10}accomplishment & \cellcolor{blue!10}narrative & \cellcolor{blue!10}grantee & \cellcolor{blue!10}outcome & \cellcolor{blue!10}objective & \cellcolor{blue!10}mod & \mybar{101} \\ 
   36 & \cellcolor{blue!10}decline & \cellcolor{blue!10}trend & \cellcolor{blue!10}recession & \cellcolor{blue!10}average & \cellcolor{blue!10}rate & \cellcolor{blue!10}percentage & \mybar{265} \\ 
   52 & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}supportive & \cellcolor{blue!10}consolidated & \cellcolor{blue!10}transitional & \cellcolor{blue!10}counseling & \mybar{193} \\ 
    1 & \cellcolor{blue!10}alderman & \cellcolor{blue!10}resolved & \cellcolor{blue!10}whereas & \cellcolor{blue!10}resolution & \cellcolor{blue!10}authorizing & \cellcolor{blue!10}authorize & \mybar{245} \\ 
   92 & \cellcolor{blue!10}concept & \cellcolor{blue!10}design & \cellcolor{blue!10}realm & \cellcolor{blue!10}visual & \cellcolor{blue!10}character & \cellcolor{blue!10}conceptual & \mybar{433} \\ 
   71 & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}proceeds & \cellcolor{blue!10}redemption & \cellcolor{blue!10}debt & \cellcolor{blue!10}series & \mybar{174} \\ 
   67 & \cellcolor{blue!10}dist & \cellcolor{blue!10}applied & \cellcolor{blue!10}col & \cellcolor{blue!10}occupancy & \cellcolor{blue!10}valuation & \cellcolor{blue!10}monoxide & \mybar{62} \\ 
   25 & \cellcolor{blue!10}scenario & \cellcolor{blue!10}figure & \cellcolor{blue!10}appendix & \cellcolor{blue!10}assume & \cellcolor{blue!10}assumption & \cellcolor{blue!10}model & \mybar{162} \\ 
   38 & \cellcolor{blue!10}horas & \cellcolor{blue!10}persona & \cellcolor{blue!10}para & \cellcolor{blue!10}yon & \cellcolor{blue!10}sou & \cellcolor{blue!10}ante & \mybar{1350} \\ 
   14 & \cellcolor{blue!10}federal & \cellcolor{blue!10}agency & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}grant & \cellcolor{blue!10}eligible & \mybar{90} \\ 
   56 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}marina & \cellcolor{blue!10}beach & \cellcolor{blue!10}port & \cellcolor{blue!10}boat & \mybar{844} \\ 
   61 & \cellcolor{blue!10}revenue & \cellcolor{blue!10}balance & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}reserve & \cellcolor{blue!10}forecast & \cellcolor{blue!10}budget & \mybar{101} \\ 
   75 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}liability & \cellcolor{blue!10}assets & \cellcolor{blue!10}statement & \cellcolor{blue!10}pension & \mybar{142} \\ 
   37 & \cellcolor{blue!10}endorse & \cellcolor{blue!10}endorsed & \cellcolor{blue!10}budget & \cellcolor{blue!10}proposed & \cellcolor{blue!10}adopted & \cellcolor{blue!10}adopt & \mybar{111} \\ 
   69 & \cellcolor{blue!10}tree & \cellcolor{blue!10}planned & \cellcolor{blue!10}circumference & \cellcolor{blue!10}gross & \cellcolor{blue!10}density & \cellcolor{blue!10}infill & \mybar{211} \\ 
   90 & \cellcolor{blue!10}councilman & \cellcolor{blue!10}introduced & \cellcolor{blue!10}ordain & \cellcolor{blue!10}ordinance & \cellcolor{blue!10}digest & \cellcolor{blue!10}yea & \mybar{244} \\ 
   97 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}grievance & \cellcolor{blue!10}employee & \cellcolor{blue!10}retirement & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}actuary & \mybar{250} \\ 
   39 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}homeowner & \cellcolor{blue!10}income & \cellcolor{blue!10}bedroom & \mybar{150} \\ 
   55 & \cellcolor{blue!10}ave & \cellcolor{blue!10}combo & \cellcolor{blue!10}blossom & \cellcolor{blue!10}pearl & \cellcolor{blue!10}cir & \cellcolor{blue!10}olive & \mybar{1091} \\ 
   13 & \cellcolor{blue!20}strategy & \cellcolor{blue!20}goal & \cellcolor{blue!20}strategic & \cellcolor{blue!20}stakeholder & \cellcolor{blue!20}focus & \cellcolor{blue!20}initiative & \mybar{162} \\ 
   57 & \cellcolor{blue!20}absent & \cellcolor{blue!20}int & \cellcolor{blue!20}preside & \cellcolor{blue!20}ordained & \cellcolor{blue!20}tag & \cellcolor{blue!20}numbers & \mybar{194} \\ 
  101 & \cellcolor{blue!20}violent & \cellcolor{blue!20}gang & \cellcolor{blue!20}firearm & \cellcolor{blue!20}offender & \cellcolor{blue!20}crime & \cellcolor{blue!20}patrol & \mybar{511} \\ 
   93 & \cellcolor{blue!80}shooting & \cellcolor{blue!80}suspect & \cellcolor{blue!80}pronounce & \cellcolor{blue!80}gunshot & \cellcolor{blue!80}flee & \cellcolor{blue!80}shoot & \mybar{730} \\ 

@@

\label{tabSTMtopwords120_2}
